\huge ARuko and Editour: \\ \Large A Platform for Augmented Reality Tour Guide Apps

### 2019-10-02 paper.tex
finish adding Ralph's suggestions
Fixed minor suggestions by Ralph, rewrote a lot of the conclusion to
separate it into three sections, and added some images. Some more images
that I don't have access to should also be added, so I created TODOs for
these

\begin{figure}[h]
	\centering
	\includegraphics[width=1\textwidth]{adobe-xd-design.png}
	\caption[A screenshot of the Adobe XD project designed by Atticus Sims]
    {A screenshot of the Adobe XD project designed by Atticus Sims}
	\label{fig:adobeXdDesign}
\end{figure}

@@

If we were ever feeling too tired to test the app by walking around, we also
mocked the GPS coordinates in software. This allowed us to simulate walking in a
single direction without actually having to build to a mobile device or move.

@@

On September 26\textsuperscript{th} we returned to Kinkaku-ji with a nearly
complete version of ARuko in order to conduct some final testing. We met up with
Atticus, the IQP group, and our friend Hikaru and installed the beta version of
ARuko on each of their phones. With little instruction about how the app works
we had each of them try going through Kinkaku-ji while listening to the tour and
using the app's features. Each member of our team also installed the beta
version so we could test it.

@@

Despite the numerous pivots this project went through, in the end we were able
to create a useful working prototype. The Editour is fully featured with
everything needed to build an audio tour anywhere in the world. ARuko allows
users to experience useful AR-enhanced tours in a pleasant and intuitive way.
Together they provide a complete platform for building augmented reality tour
guide apps.

@@

@@

Despite these issues our team is happy with the product we delivered to
Kyoto~VR. Selling ARuko on app stores was not within the scope of our academic
project, but we were able polish the app enough such that it would be feasible
for Atticus to eventually sell the app. The UI could use more testing with real
users to make sure it is intuitive and easy to use. We also intended to add a
feature where the app could automatically download tour files from the Editour
server and import them without having to rebuild. We were not able to complete
this feature due to time constraints, but it could easily be added because all
of ARuko's business logic is abstracted and generalized to support multiple
tours. Editour also already supports requesting and downloading the most recent
versions of tours.

@@

\clearpage % references should be on their own page

@@

% for tabularx
% \newcolumntype{L}{>{\raggedright\arraybackslash\footnotesize}X}%

\begin{table}[h]
\begin{singlespace}
\begin{tabulary}{\textwidth}{ L | L | L | L | L | L }
	I enjoyed the audio tour & The image gallery added to the audio tour & I
	found the AR translation feature helpful & I found the AR map overlay
	helpful & The AR features were easy to use & Do you have any other thoughts
	on how to improve the experience? \\
	\hline

>>>>

% TODO split up this figure into four separate figures, change references to
% refer to the correct ones
\begin{figure}[h]
	\centering
	\includegraphics[width=1\textwidth]{adobe-xd-design.png}
	\caption[A screenshot of the Adobe XD project designed by Atticus Sims]
    {A screenshot of the Adobe XD project designed by Atticus Sims}
	\label{fig:adobeXdDesign}
\end{figure}

@@

To maximize testing efforts and negate having to physically walk around we also
simulated the GPS coordinates in software. This allowed us to simulate walking
in a single direction without actually having to build to a mobile device or
move.

@@

On September 26\textsuperscript{th} we returned to Kinkaku-ji with a nearly
complete version of ARuko in order to conduct some final testing. We met up with
Atticus, the IQP group, and our friend Hikaru and installed the beta version of
ARuko on each of their phones. With little instruction about how the app works
we had each of them try going through Kinkaku-ji while listening to the tour and
using the app's features. Each member of our team also installed the beta
version so we could test it. % TODO add photos of us testing it

@@

Our team is satisfied with the final result of this project, as we feel we have
built a working platform that Kyoto VR will easily be able to build off of in
the future. This section contains our final thoughts on the project and future
work that could be done on it.

\subsection{What Went Wrong}
\label{sec:whatWentWrong}

@@

On a similar note, the requirements and scope of the project changed greatly
from week to week, and sometimes even within one day. We spent a lot of time
exploring concepts and features that were completely unrelated to the final
product. We also did not receive official specifications, such as the design of
the GUI Atticus wanted for the app, until very late in the development process.

@@

While not a disaster, we had some initial trouble getting started with Unity.
Different versions of Unity do not play well with each other, and it often runs
into bugs on older hardware, such as the laptops we had to work with.
Furthermore, a stable version of the Unity editor is not available on
GNU/Linux~\autocite{best2019}, so one of our team members had to install MacOS
in order to use it. We were able to resolve these issues in the first weeks of
the project, but it consumed some of our valuable time in July.

\subsubsection{What Went Well}
\label{sec:whatWentWell}

Despite these issues, in the end we were able to create a useful working
prototype. The Editour is fully featured with everything needed to build an
audio tour anywhere in the world. ARuko allows users to experience useful
AR-enhanced tours in a pleasant and intuitive way. Together they provide a
complete platform for building augmented reality tour guide apps.

Editour was not initially a requirement that Atticus had in mind, but it turned
out to be a very useful tool in designing tours and allowing the app to be
extensible. Two members of our team, Cole Granof and Joseph Petitti, had
experience building web applications with HTML, CSS, and JavaScript, and the
Editour allowed them to use these skills to help the project.

Our team's broad range of skills made it so that each member had specific tasks
that they were good at. This made the division of labor easier, and throughout
the project we never had issues splitting up work.

The research time we put in at the beginning of the project also proved to be
very useful. Our decision to use Unity Vuforia based on this research made
implementing many of the complex AR features easier later on. If we had chosen a
less-ideal platform, we might have had to switch to a different one after
wasting time on that poor decision.

\subsubsection{Future Work}
\label{sec:futureWork}

Although selling ARuko on app stores was not within the scope of our academic
project, but we were able polish the app enough such that it would be feasible
for Atticus to eventually sell the app. The UI could use more testing with real
users to make sure it is intuitive and easy to use. We also intended to add a
feature where the app could automatically download tour files from the Editour
server and import them without having to rebuild. We were not able to complete
this feature due to time constraints, but it could easily be added because all
of ARuko's business logic is abstracted and generalized to support multiple
tours. Editour also already supports requesting and downloading the most recent
versions of tours.

@@

@@

\begin{table}[h]
\begin{singlespace}
\renewcommand{\arraystretch}{2.0} % add space between rows
\footnotesize % make font smaller
\begin{tabulary}{\textwidth}{ L | L | L | L | L | L }
	I enjoyed the audio tour & The image gallery added to the audio tour & I
	found the AR translation feature helpful & I found the AR map overlay
	helpful & The AR features were easy to use & Do you have any other thoughts
	on how to improve the experience? \\
	\hline
